Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-25 documentation/paper.tex
Explained precision/recall and completed one table accordingly

Class-wise standard deviation captures how decisive the network is: whether its prediction is confidently high or low, or is only slightly closer to one edge of the spectrum.

Numerically, this is a variable defined as $C$ below, where $N$ and $A$ are the sets of outputs of the supervised learning discriminator in question, corresponding to the sets of neutrons and alpha particles respectively (or calibration and background sets respectively, depending on which is used as ground truth data). It calculates the spread of the network's predictions for each ground truth class. This means that a decisive discriminator, which produces a wide separation between the two classes, is preferred over one that produces a nebulous cloud of outputs with a seemingly arbitrary decision boundary.

@@

$C=(std(N \div S) + std(A \div S)) \div 2$

@@

\begin{center}
    \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
        \hline
        0.003 & 0 & 24 & 3 & 3 & 95\% & 0.44 \\
        \hline
        0.003 & 0 & 48 & 5 & 3 & 96\% & 0.41 \\
        \hline
        0.003 & 0.5 & 24 & 5 & 3 & 93\% & 0.50 \\
        \hline
        0.001 & 0 & 48 & 5 & 3 & 95\% & 0.48 \\
        \hline
        0.001 & 0.25 & 48 & 3 & 6 & 93\% & 0.62 \\
        \hline
        0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 0.49 \\
        \hline
    \end{tabular}

>>>>

The correctness of the network's predictions is further detailed in the precision and recall statistics. Precision represents the proportion, of those that the network predicts to be nuclear recoils, that are actually nuclear recoils (or part of the corresponding calibration set). It is an indicator of how pure the network's predictions are for the recoil class. Recall represents the proportion, of those that are actually nuclear recoils, that the network predicts to be nuclear recoils. It indicates how many examples the network misses (i.e., those that would erroneously be removed as background radiation).

Class-wise standard deviation, abbreviated CWSD, captures how decisive the network is: whether its prediction is confidently high or low, or is only slightly closer to one edge of the spectrum.

Numerically, this is a variable defined below, where $N$ and $A$ are the sets of outputs of the supervised learning discriminator in question, corresponding to the sets of neutrons and alpha particles respectively (or calibration and background sets respectively, depending on which is used as ground truth data). It calculates the spread of the network's predictions for each ground truth class. This means that a decisive discriminator, which produces a wide separation between the two classes, is preferred over one that produces a nebulous cloud of outputs with a seemingly arbitrary decision boundary.

@@

$CWSD=(std(N \div S) + std(A \div S)) \div 2$

@@

\begin{center}
    \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Filters & Kernel & Layers $\times$ & Max Accuracy & Precision & Recall & CWSD \\
        \hline
        0.003 & 0 & 24 & 3 & 3 & 95\% & 99\% & 85\% & 0.44 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1533824431_epoch30.json
        \hline
        0.003 & 0 & 48 & 5 & 3 & 96\% & 99\% & 89\% & 0.41 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533825716_epoch43.json
        \hline
        0.003 & 0.5 & 24 & 5 & 3 & 93\% & 98\% & 83\% & 0.50 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1533828588_epoch27.json
        \hline
        0.001 & 0 & 48 & 5 & 3 & 95\% & 98\% & 87\% & 0.48 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533832229_epoch16.json
        \hline
        0.001 & 0.25 & 48 & 3 & 6 & 93\% & 94\% & 91\% & 0.62 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters48_kernel_size3_convolutional_layers_per_group6time1533834812_epoch30.json
        \hline
        0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 97\% & 91\% & 0.49 \\
        % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group6time1533849077_epoch45.json
        \hline
    \end{tabular}
